### 2019-01-15 Sections/economics_of_the_quantum_internet.tex
minor

Now, quantum computing uses similar strategies for possible solutions, with one key difference. Using classical computing, the relationship for the \textsc{Unify} strategy was described as additive in nature, where the computational resources of both players are accumulated additively when unified into a larger virtual computer. In the corresponding quantum \textsc{Unify} strategy, this effect is enhanced by their super-linear computational leverage. For the sake of illustration, we will now assume this becomes multiplicative\footnote{In practise, a complete formalism would be expressed in terms of arbitrary computational scaling functions, $f_\mathrm{sc}$ (Sec.~\ref{sec:comp_sc_func}).}. As such, should $X$ and $Y$ build identical quantum computers, the hypothesised payoff matrix would become as shown in Tab.~\ref{tab:game_theory_2}.

@@

\subsection{Cooperative enhancement}\index{Cooperative enhancement}

@@

The final point is particularly noteworthy, since it implies that optimal game-theoretic outcomes are not objective, but subjective, and highly dependent on how players are employing their computational resources, which may be highly asymmetric. If one player is employing an exponential scaling function, whereas the other is only employing a polynomial one, this could completely distort the dynamics of the game in favour of the player who would otherwise have been weaker under symmetric scaling functions. This in turn could completely alter the landscape of how users choose to optimally play.

>>>>

Now, quantum computing uses similar strategies for possible solutions, with one key difference. Using classical computing, the relationship for the \textsc{Unify} strategy was described as additive in nature, where the computational resources of both players are accumulated additively when unified into a larger virtual computer. In the corresponding quantum \textsc{Unify} strategy, this effect is enhanced by their super-linear computational leverage. For the sake of illustration, we will now assume this becomes multiplicative. As such, should $X$ and $Y$ build identical quantum computers, the hypothesised payoff matrix would become as shown in Tab.~\ref{tab:game_theory_2}.

@@

\subsection{Cooperative payoff enhancement}\index{Cooperative payoff enhancement}

@@

The final point is particularly noteworthy, since it implies that optimal game-theoretic outcomes are not objective, but subjective, and highly dependent on how players are employing their computational resources, which may be highly asymmetric. If one player is employing an exponential scaling function, whereas the other is only employing a polynomial one, this could completely distort the utility payoff dynamics of the game in favour of the player who would otherwise have been weaker under symmetric scaling functions. This in turn could completely alter the landscape of how users choose strategies to play optimally.
